systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-11-23 paper/trunk/systemfit_estimation.tex
added notes that the formulas to calculate 2SLS, W2SLS, and 3SLS estimators and their covariances can be obtained from the formulas to calculate OLS, WLS, and SUR estimators and their covariances by substituting fitted regressors for the original regressors
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@838 591db2bd-e0a0-4d22-8c19-2192dbb7da31

At the first stage new ('fitted') regressors are obtained by
\begin{equation}
   \XHat_i = H_i \left( H_i' H_i \right)^{-1} H_i' X .
\end{equation}
Then, these 'fitted' regressors are used
to obtain unbiased 2SLS, W2SLS, or 3SLS estimates of $\beta$ by
\begin{equation}
   \bHat
   = \left( \XHat' \OHat^{-1} \XHat \right)^{-1} \XHat' \OHat^{-1} y .
   \label{eq:2sls-w2sls-3sls}
\end{equation}
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat \right]
   = \left( \XHat' \OHat^{-1} \XHat \right)^{-1} .
   \label{eq:cov-2sls-w2sls-3sls}
\end{equation}

>>>>

At the first stage new ('fitted') regressors are obtained by
\begin{equation}
   \XHat_i = H_i \left( H_i' H_i \right)^{-1} H_i' X .
\end{equation}
Then, these 'fitted' regressors are substituted for the original regressors
in equation~(\ref{eq:ols-wls-sur})
to obtain unbiased 2SLS, W2SLS, or 3SLS estimates of $\beta$ by
\begin{equation}
   \bHat
   = \left( \XHat' \OHat^{-1} \XHat \right)^{-1} \XHat' \OHat^{-1} y .
   \label{eq:2sls-w2sls-3sls}
\end{equation}
An estimator of the covariance matrix of the estimated parameters
can be obtained from equation~(\ref{eq:cov-ols-wls-sur}) analogously.
Hence, we get
\begin{equation}
   \COVHat \left[ \bHat \right]
   = \left( \XHat' \OHat^{-1} \XHat \right)^{-1} .
   \label{eq:cov-2sls-w2sls-3sls}
\end{equation}
